---
title: "Class_10_29"
author: "Elizabeth Guo"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(moderndive)
library(infer)
library(googlesheets4)
library(fs)
library(scales)
library(gt)
library(tidyverse)
```


```{r, message= FALSE}
sheets_deauth()

sampling <- read_sheet("1cgP-e6THVfiW5TJ95QhX3jkNxKvc8Sicp9k_BkSRd2I") %>% 
  mutate(red_proportion = red/25) %>% 
  drop_na()

OG <-  ggplot(sampling, aes(x = red_proportion)) +
    geom_histogram(binwidth = .04, col = "white") + 
    labs(title = "Distribution of Proportion of Red Beads Found in Group of 25 Beads", 
         x = "Proportion of Red Beads") 
OG
```


```{r, message=FALSE}
sheets_deauth()

trains <- read_sheet("1QV7o63fiZdNtMtLQfdwREapf8eYDjpfSRX0dgfNrB8A")
```

```{r, message= FALSE}
urn <- tibble(bead = c(rep("Red", 2000), rep("White", 8000)))


prop_red <- urn %>%
  rep_sample_n(size = 25, reps = 1000, replace = TRUE) %>% 
  group_by(replicate) %>% 
  summarize(red = sum(bead == "Red")) %>% 
  mutate(prop_red = red / 25)


P <- ggplot(prop_red, aes(x = prop_red)) + geom_histogram(binwidth = .04, col = "white") + 
    labs(title = "RED",
         x = "Proportion of Red Beads",
         y = "Count")
P
```

prop_crimson_graph <- bowl %>%
  rep_sample_n(size = 25, reps = 5000) %>% 
  group_by(replicate) %>% 
  summarize(crimson = sum(bead == "crimson")) %>% 
  mutate(prop_crimson = crimson / 25)

  # I used rep_sample_n in order to simulate repeating the action of drawing 25 times. 

  ggplot(prop_crimson_graph, aes(x = prop_crimson)) + geom_histogram(binwidth = .05) + 
    labs(title = "Distirbution of Proportion of Crimson Beads Found in Group of 25 Beads",
         x = "Proportion of Crimson Beads") +
    theme_light()
  
  # This is my ggplot with appropriate labels. I also changed the theme color. 




